TODO

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: added some changes in verification

  There are different approaches for the verification of the P4 programs. There are tools, which uses symbolic execution \cite{vera}, or SMT solver \cite{p4v, bf4}. The reason we insert the verification into this tool is that we would like to create a universal framework to help the P4 developers in their work and have an assistant analysis, which helps in error detection.

@@

  In Figure \ref{code:cond}, there is an example condition for the MyIngress. We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition is true, and the table executes one of the possible actions i.e. $\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition is false.

@@

  This calculation is built into the tool as an application, which uses the call-graph and the control-flow graph analyzes of the experts. The method can combine these two graphs, and while traversing them, it calculates the condition pair for the vertices of the call graph, while getting the information for it from the control flow graph.

>>>>

@@

  In Figure \ref{code:cond}, there is an example condition for the MyIngress. We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition of the branch is true, and the table executes one of the possible actions i.e. $\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition of the branch is false.

@@

   This calculation is built into the tool as an application. It uses two experts: the call graph and control-flow graph. While traversing through the call graph it can reach calls of tables and actions. When it reaches a call, it starts to traverse through the proper subgraph of the control-flow graph and calculates the conditions of the actual block. Every condition is stored in the graph as a property of the called vertex of the call graph. 
   The implementation gets and saves every information about the program with Gremlin queries.
